Applications of the Fresnel Integrals

### 2019-03-17 draft.tex
the second app

 is used in the theory of driving motorcar round a corner quickly.

 The Euler spiral also provides optimal curvature for train tracks between a straight run and an upcoming bend.

\section{Conclusion}

>>>>

An object traveling on a circular path experiences a centripetral acceleration. The same happens when a train that travels on a straight path suddenly transitions to a tangential circular path. This sudden centripetal acceleration causes much discomfort for the driver as well as the passengers on the train.

In order to provide a smooth riding experience, much effort has been made in the history of railway construction. According to \cite{Lev08}, Mr. Gravatt was the first one who designed a sine curve around the year of 1828. Later by 1842, William Froude proposed to use a curve approximating the elastic curve, for the purpose of making the change of curvature by degree. In the year of 1880, Charles Crandall gives priority for the "true transition curve" to Ellis Holbrook in the Railroad Gazette. However, Arthur Talbot was among the first to approach the problem mathematically as he describes the problem and his solution in the introduction to "The Railway Transition Spiral" \cite{Tal99}:

\begin{quotation}
	A transition curve, or easement curve, as it is sometimes called, is a curve of varying radius
	used to connect circular curves with tangents for the purpose of avoiding the shock and
	disagreeable lurch of trains, due to the instant change of direction and also to the sudden
	change from level to inclined track. The primary object of the transition curve, then, is to
	effect smooth riding when the train is entering or leaving a curve.

	The generally accepted requirement for a proper transition curve is that the degree-of-curve
	shall increase gradually and uniformly from the point of tangent until the degree of the main
	curve is reached, and that the super-elevation9
	shall increase uniformly from zero at the
	tangent to the full amount at the connection with the main curve and yet have at any point
	the appropriate super-elevation for the curvature. In addition to this, an acceptable transition
	curve must be so simple that the field work may be easily and rapidly done, and should be so
	flexible that it may be adjusted to meet the varied requirements of problems in location and
	construction.
\end{quotation}

Given the expression of centripetal acceleration $V^{2} / R$, the obvious solution is to provide an easement curve whose curvature, $1/R$, increases linearly with the traveled distance. This geometry is an Euler spiral.

Unaware of the solution of the geometry by Leonhard Euler, Rankine cited the cubic curve (a polynomial curve of degree 3), which is an approximation of the Euler spiral for small angular changes in the same way that a parabola is an approximation to a circular curve.

Marie Alfred Cornu (and later some civil engineers) also solved the calculus of Euler spiral independently. Euler spirals are now widely used in rail and highway engineering for providing a transition or an easement between a tangent and a horizontal circular curve.

\section{Conclusion}
The Euler spiral is a well known mathematical curve which can be constructed by peeling an orange around the spiral with a kitchen knife. Fresnel integrals are the mathematical equations that describe the Euler spiral. In this paper, we mainly study the properties of the Fresenal integrals and its two major applications: Fresnel Diffraction and railway transition curve construction.
